ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-03-30 pyked.tex
updated references and style

%====================================================================
\section{Introduction}
%
Fundamental combustion experiments provide vital data for understanding fuel
chemistry and validating chemical kinetic models. Important measured quantities
include autoignition delay times, laminar flame speeds, and species profiles,
among others. However, despite both the importance and abundance of such
information in the literature, the combustion\slash chemical kinetics community
lacks an accepted, commonly used standard for recording and sharing data from
fundamental combustion experiments.\footnote{Interestingly, this contrasts the
situation for chemical kinetic models, where the CHEMKIN~\autocite{Kee:1996ck}
format dominates. Competing standards such as the
Cantera~\autocite{Cantera:2.3.0} CTI format or
FlameMaster~\autocite{FlameMaster:ref,FlameMaster:code} lag behind considerably,
although use of the former continually grows due to Cantera's open availability.
% Similarly, % with more space, discuss JANAF/NASA polynomial standard ?
}

>>>>

%====================================================================
\section{Introduction}
%
Fundamental combustion experiments provide vital data for understanding fuel
chemistry and validating chemical kinetic models. Important measured quantities
include autoignition delay times, laminar flame speeds, and species profiles,
among others. However, despite both the importance and abundance of such
information in the literature, the combustion\slash chemical kinetics community
lacks an accepted, commonly used standard for recording and sharing data from
fundamental combustion experiments.\footnote{Interestingly, this contrasts the
situation for chemical kinetic models, where the CHEMKIN~\autocite{Kee:1996ck}
format dominates. Competing standards such as the
Cantera~\autocite{Cantera:2.3.0} CTI format or
FlameMaster~\autocite{FlameMaster:ref} lag behind considerably,
although use of the former continually grows due to Cantera's open availability.
% Similarly, % with more space, discuss JANAF/NASA polynomial standard ?
}
